Response to reviewers

### 2018-02-01 manuscripts/AmNat_response_to_rev.Rmd

As the editor notes, we suspect that Reviewer 1's simulations are not indeed identical except in the way mentioned, since they appear to assume the optimal policy can be specified in terms of a single constant escapement. Our results and in general escapement need not be constant but will depend on the observed stock size an on previous measurements, as we now emphasize.  Also as the editor notes, the Reviewer's description of what they have done is extremely brief and thus difficult to be sure we have characterized precisely, but nevertheless, we believe our analysis sheds some light on why the reviewer finds this paradoxical conclusion while our analysis does not.

@@

The reviewer and editor have raised an important issue in the question of whether we permit the harvest quota to be set to a value higher than the stock.  There are two problems with this.  First, it's not clear how the reviewer implements this assumption in the face of measurement uncertainty: how can one be certain a quota is less than 90% of stock size X without knowing what X is?  One can obviously enforce this with respect to the measured stock size but not the true stock size.  More importantly, this assumption amounts to the assertion that it is mathematically impossible to over-fish a stock to the point of collapse.  However low the stock size might get, local extinction is impossible.  In this world-view, there will always be some tiny fraction of ato-fishes from which the population can recover.  Assuming that local extinction is impossible will indeed bias any optimal decision model to be more aggressive.  Obviously this also has implications for ecological models in general, conservation policy would look different if we assumed extinction was impossible. @Clark1986 already recognized that a very similar assumption in @Reed1979 derivation that stochastic models needed no additional caution ($S=D$) was likely due to the fact that accidentally extinction was impossible (see manuscript, line 150). We do not adopt this assumption.  Obviously real world populations cannot be indefinitely reduced by only a fractional percentage. In our simulations, though we consider a Ricker model, stock abundances are divided into 100 distinct bins, with the smallest bin corresponding to a stock size of zero. Thus it is possible for over-harvesting or stochastic environment, or some combination of both, to lead a population to permanently collapse once it has gotten small enough.

@@

We thank the Reviewer for this careful parallel investigation, which was very useful in focusing the manuscript on some of the key results.  We believe the differences in our respective results can be explained by the differences in our methods as discussed in our reply to the Editor's discussion of this issue. In short, we believe the reviewer's seemingly counter-intuitive result that increased uncertainty should be met with an action (lowering escapement) that would increase the risk of stock collapse rather then the intuitive response to be cautious by reducing harvest, is simply an artifact of the reviewer's assumption that stock collapse is impossible, and thus increased harvesting poses no real risk.

>>>>

As the editor notes, we suspect that Reviewer 1's simulations are not indeed identical except in the way mentioned, since they appear to assume the optimal policy can be specified in terms of a single constant escapement. Our results and in general escapement need not be constant but will depend on the observed stock size and on previous measurements, as we now emphasize.  Also as the editor notes, the Reviewer's description of what they have done is extremely brief and thus difficult to be sure we have characterized precisely, but nevertheless, we believe our analysis sheds some light on why the reviewer finds this paradoxical conclusion while our analysis does not.

@@

The reviewer and editor have raised an important issue in the question of whether we permit the harvest quota to be set to a value higher than the stock.  There are two problems with this.  First, it's not clear how the reviewer implements this assumption in the face of measurement uncertainty: how can one be certain a quota is less than 90% of stock size X without knowing what X is?  One can obviously enforce this with respect to the measured stock size but not the true stock size.  More importantly, this assumption amounts to the assertion that it is mathematically impossible to over-fish a stock to the point of collapse.  However low the stock size might get, local extinction is impossible.  In this world-view, there will always be some tiny fraction of ato-fishes from which the population can recover.  Assuming that local extinction is impossible will indeed bias any optimal decision model to be more aggressive.  Obviously this also has implications for ecological models in general, conservation policy would look different if we assumed extinction was impossible. @Clark1986 already recognized that a very similar assumption in @Reed1979 derivation that stochastic models needed no additional caution ($S=D$) was likely due to the fact that accidentally extinction was impossible (see manuscript, line 150). We do not adopt this assumption.  Obviously real world populations cannot be indefinitely reduced by only a fractional percentage. In our simulations, though we consider a Gordon-Schaefer model, stock abundances are divided into 100 distinct bins, with the smallest bin corresponding to a stock size of zero. Thus it is possible for over-harvesting or stochastic environment, or some combination of both, to lead a population to permanently collapse once it has gotten small enough.

@@

We thank the Reviewer for this careful parallel investigation, which was very useful in focusing the manuscript on some of the key results.  We believe the differences in our respective results can be explained by the differences in our methods as discussed in our reply to the Editor's discussion of this issue. In short, we believe the reviewer's seemingly counter-intuitive result that increased uncertainty should be met with an action (lowering escapement) that would increase the risk of stock collapse rather than the intuitive response to be cautious by reducing harvest, is simply an artifact of the reviewer's assumption that stock collapse is impossible, and thus increased harvesting poses no real risk.
